---
title: "Introduction to fishi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fishi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, warning = FALSE, include = FALSE}
library(fishi)
library(codama)
library(furdeb)
library(readxl)
library(readr)
library(kableExtra)

# Database connection
config <- configuration_file(path_file = paste0(path.expand("~"),"/.appconfig/indicator_glossary/configuration_file_fishi.yml"),
                             silent = TRUE)
balbaya_con <- postgresql_dbconnection(db_user = config[["databases_configuration"]][["balbaya_vmot5"]][["login"]],
                                                          db_password = config[["databases_configuration"]][["balbaya_vmot5"]][["password"]],
                                                          db_dbname = config[["databases_configuration"]][["balbaya_vmot5"]][["dbname"]],
                                                          db_host = config[["databases_configuration"]][["balbaya_vmot5"]][["host"]],
                                                          db_port = config[["databases_configuration"]][["balbaya_vmot5"]][["port"]])
```

# Indicators

All the fishi indicators work in the same way. Each function has several arguments :

-   **data_connection:** connection to the database of your choice, it must be a list [database name, database connection link].

-   **time_period:** the time period selected for the indicator

-   **ocean:** code for the ocean of your choice (cf referentials)

-   **country:** code for the country of your choice (cf referentials)

-   **graph_type:** plot or plotly for a dynamic figure

-   **vessel_type_select:** to select the precision of the vessels

-   **vessel_type:** vessel code (for seiners, if vessel_type_select = "engin" choose 1, if vessel_type_select = "vessel_type" choose 4, 5, 6.\

    ## Fishing capacity : Atlantic Ocean, 1991-2022

```{r, message=FALSE, warning=FALSE, fig.width = 8, fig.height = 8}
fishing_capacity(data_connection = balbaya_con,
                 time_period = as.integer(c(1991:2022)), 
                 ocean = as.integer(1),
                 graph_type = "plot",
                 vessel_type_select = "vessel_type",
                 vessel_type = as.integer(x = c(4, 5, 6)),
                 figure = "vessel")
```

## Fishing capacity : Indian ocean, 1981-2022

```{r, message=FALSE, warning=FALSE, fig.width = 8, fig.height = 8}
fishing_capacity(data_connection = balbaya_con,
                 time_period = as.integer(c(1981:2022)), 
                 ocean = as.integer(2),
                 graph_type = "plot",
                 vessel_type_select = "vessel_type",
                 vessel_type = as.integer(x = c(4, 5, 6)),
                 figure = "vessel")
```

# Referentials

### Country

```{r, echo = FALSE}
code <- c(1, 41)
country <- c("French", "Mayotte")
color <- c("#a6cee3", "#1f78b4")
tableau <- data.frame(code, country, color)

kable(tableau, "html") %>%
  kable_classic(c("hover",
                  "condensed"), 
                font_size = 14) %>%
  row_spec(1, color = "white", background = "#a6cee3") %>%
  row_spec(2, color = "white", background = "#1f78b4")
```

### Ocean

```{r, echo = FALSE}
code <- c(1, 2, 3, 4, 5)
ocean <- c("Atlantic", "Indian", "Western Pacific", "East Pacific", "Pacific")
color <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99")
tableau <- data.frame(code, ocean, color)

kable(tableau, "html") %>%
  kable_classic(c("hover",
                  "condensed"), 
                font_size = 14) %>%
  row_spec(1, color = "white", background = "#a6cee3") %>%
  row_spec(2, color = "white", background = "#1f78b4") %>%
  row_spec(3, color = "white", background = "#b2df8a") %>%
  row_spec(4, color = "white", background = "#33a02c")%>%
  row_spec(5, color = "white", background = "#fb9a99")
```

### Specie

```{r, echo = FALSE}
data <- data.frame(
  code = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 18, 100),
  name = c("YFT", "SKJ", "BET", "ALB", "LTA", "FRI", "SHX", "DSC", "MIX", "KAW", "FRZ", "Other"),
  full_name = c("Yellowfin tuna", "Skipjack tuna", "Bigeye tuna", "Albacore tuna", "Little tuna", "Frigate tuna", "Sharks", "Discard tuna", "Mixed species of tuna", "Mackerel tuna", "Ray-finned bony fish", "Other"),
  color = c("#FFD700", "#00688b", "#ee2c2c", "#f4a261", "#332288", "#44AA99", "#661100", "#AA4499", "#ff9f1c", "#6699CC", "#999933", "#8d99ae")
)

kable(data, "html") %>%
  kable_classic(c("hover",
                  "condensed"), 
                font_size = 14) %>%
  row_spec(1, color = "white", background = "#FFD700") %>%
  row_spec(2, color = "white", background = "#00688b") %>%
  row_spec(3, color = "white", background = "#ee2c2c") %>%
  row_spec(4, color = "white", background = "#f4a261") %>%
  row_spec(5, color = "white", background = "#332288") %>%
  row_spec(6, color = "white", background = "#44AA99") %>%
  row_spec(7, color = "white", background = "#661100") %>%
  row_spec(8, color = "white", background = "#AA4499") %>%
  row_spec(9, color = "white", background = "#ff9f1c") %>%
  row_spec(10, color = "white", background = "#6699CC") %>%
  row_spec(11, color = "white", background = "#999933") %>%
  row_spec(12, color = "white", background = "#8d99ae")
```

### Boat

```{r, echo = FALSE}
data <- data.frame(
  code_vessel_type = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 99),
  code_engin = c(2, 2, 5, 1, 1, 1, 3, 4, 4, 4, 4, 2, 0),
  name = c("Canne/glacier", "Canne/congélateur", "Mixte", "Senneur avec appât", "Senneur sans appât", "Grand senneur", "Palangrier", "Bateau Mère", "Bateau Usine", "Supply", "Cargo", "Canneur/supply", "Inconnu"))

kable(data, "html") %>%
  kable_classic(c("hover",
                  "condensed"), 
                font_size = 14)
```

# Tableaux de données

The databases and csv used by fishi contain a large number of columns. To be able to use the functions, you need to provide a dataset with identical column names. Here's what they correspond to :

**activity_date** : Date of activity (boat out of service, transit, catch+ and catch+ weight, etc.). It is entered in dd/mm/yyyy format. The first record should correspond to the departure date for a trip.

**catch** : Weight of fish caught during the current activity (commercial or non-commercial species, stored in tanks or dumped at sea).

**c_bat** : The boat's internal code (note that the same boat may have several different codes when changing flag, etc.).

**c_esp** : Internal species code

**country_id** : Code of the country

**c_tban** : School type code.

**c_quille** : Keel coding (unique throughout the ship's life).

**cwp11_act** : code of the 1x1 square in which the activity is located

**fleet** : Country's fleet.

**flag** : Country's flag.

**gear** : Name for type of vessel used.

**landing_date** : Boat landing date (dd/mm/yyyy format).

**l_bat** : Name of the ship.

**n_act** : Numeric identifier of the activity (from 1 to n). This is the only field that can be used to differentiate one activity from another for the same day of the week. Note that an increasing range of numbers does not necessarily correspond to the chronological range.

**ocean_id** : Code of the ocean in which the geographical area is located

**ocean_name** : Name of the ocean in which the geographical area is located

**port** : Port designation (ORSTOM)

**v_tpec** : Total hours fished during the activity (= set +search +transit etc.). Approximately 12h in OA and 13h in OI. Note that if several activities take place on the same date, the first will take the total hours and the others 0.

**v_tmer** : Total hours at sea for the activity (from 0 to 24h). Note that if several activities take place on the same date, the first will take 24h and the others 0.

**v_dur_cal** : set duration calculated using several parameters: fishing method, tonnage and fishing year

v_nb_calees : total number of sets during the activity.

v_nb_calee_pos : total number of positive sets during the activity.

**vessel_type_id** : Code for type of vessel used

**l4c_tban** : Abbreviated name of school type

sardara :

cl

v_mensur

c_banc

c_esp

an

ocean_id

country_id
