---
title: "referentials"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{referentials}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fishi)
library(kableExtra)
```

The fishi package uses several referential : specie, ocean, vessel type and country. Each of them is defined by a code, an integer, a name and an associated colour. In this vignette, we will see the different referential and what they include.

### Specie

The database contains 11 different species but the main ones are YFTRUE, SKJ and BET. The following table shows the 11 species and their associated colours.

```{r Specie - code, echo=FALSE}
specie <- read.delim("E:/git/fishi/inst/referential/specie.txt", sep = ";")

kbl(specie) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(1, bold = TRUE, color = "white", background = "#DDCC77") %>%
  row_spec(2, bold = TRUE, color = "white", background = "#CC6677") %>%
  row_spec(3, bold = TRUE, color = "white", background = "#88CCEE") %>%
  row_spec(4, bold = TRUE, color = "white", background = "#117733") %>%
  row_spec(5, bold = TRUE, color = "white", background = "#332288") %>%
  row_spec(6, bold = TRUE, color = "white", background = "#AA4499") %>%
  row_spec(7, bold = TRUE, color = "white", background = "#661100") %>%
  row_spec(8, bold = TRUE, color = "white", background = "#44AA99") %>%
  row_spec(9, bold = TRUE, color = "white", background = "#ff9f1c") %>%
  row_spec(10, bold = TRUE, color = "white", background = "#6699CC") %>%
  row_spec(11, bold = TRUE, color = "white", background = "#999933")
```

### Ocean

The following table shows the 5 oceans and their associated colours. This table explains the coding of the major oceanic zones (1: Atlantic Ocean, 2: Indian Ocean, etc.) as described by ORSTOM and kept by CRH.

```{r Ocean - code, echo=FALSE}
ocean <- read.delim("E:/git/fishi/inst/referential/ocean.txt", sep = ";")

kbl(ocean) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(1, bold = TRUE, color = "white", background = "#a6cee3") %>%
  row_spec(2, bold = TRUE, color = "white", background = "#1f78b4") %>%
  row_spec(3, bold = TRUE, color = "white", background = "#b2df8a") %>%
  row_spec(4, bold = TRUE, color = "white", background = "#33a02c") %>%
  row_spec(5, bold = TRUE, color = "white", background = "#fb9a99")
```

### Vessel type

The following table shows the 5 vessel types and their associated colours. This table records the types of gear encountered in the fisheries under consideration.

```{r Balbaya vessel type - code, echo=FALSE}
balbaya_vessel <- read.delim("E:/git/fishi/inst/referential/balbaya_vessel_simple_type.txt", sep = ";")

kbl(balbaya_vessel) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(1, bold = TRUE, color = "white", background = "#a6cee3") %>%
  row_spec(2, bold = TRUE, color = "white", background = "#1f78b4") %>%
  row_spec(3, bold = TRUE, color = "white", background = "#b2df8a") %>%
  row_spec(4, bold = TRUE, color = "white", background = "#33a02c") %>%
  row_spec(5, bold = TRUE, color = "white", background = "#fb9a99")
```

```{r T3 vessel type - code, echo=FALSE}
t3_vessel <- read.delim("E:/git/fishi/inst/referential/t3_vessel_simple_type.txt", sep = ";")

kbl(t3_vessel) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(1, bold = TRUE, color = "white", background = "#a6cee3") %>%
  row_spec(2, bold = TRUE, color = "white", background = "#1f78b4") %>%
  row_spec(3, bold = TRUE, color = "white", background = "#b2df8a") %>%
  row_spec(4, bold = TRUE, color = "white", background = "#33a02c") %>%
  row_spec(5, bold = TRUE, color = "white", background = "#fb9a99") %>%
  row_spec(6, bold = TRUE, color = "white", background = "#fdbf6f")
```

### 

### Country

The following table shows the 2 countries and their associated colours. Here the code is an internal numerical code, which does not refer to any national or international list.

```{r Country - code, echo=FALSE}
country <- read.delim("E:/git/fishi/inst/referential/country.txt", sep = ";")

kbl(country) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(1, bold = TRUE, color = "white", background = "#a6cee3") %>%
  row_spec(2, bold = TRUE, color = "white", background = "#1f78b4")
```
